---
title: "P8105 Homework 1"
author: Jasmine Niu (jn2855)
output: github_document
---

```{r}
library(tidyverse)
```

## Problem 1

### Load the "penguins" dataset

```{r}
data("penguins", package = "palmerpenguins")
```

### Write a short desciption of the "penguins" dataset

* The dataset "penguins" have 344 samples. There are 8 variables in total: species, the island the each penguin lives on, the bill length, the bill depth, the flipper length, body mass, sex, and year (of their birth, I suppose).

* The size of the dataset: there are 344 rows and 8 columns in this dataset.(Please refer to the R codes below.)

```{r}
nrow(penguins)
ncol(penguins)
```
* The mean flipper length is 200.9152 mm. (Please refer to the R codes below.)

```{r}
mean(penguins$flipper_length_mm, na.rm = TRUE)
```
### Make a scatterplot and export my first scatterplot to my project directory

```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color(species))) + geom_point()
ggsave("scatter_plot_hw1_jn2855.pdf", height = 4, width = 6)
```

