---
title: "P8105 Homework 1"
author: Jasmine Niu (jn2855)
output: github_document
---

```{r}
library(tidyverse)
```

## Problem 1

### Load the "penguins" dataset

```{r}
data("penguins", package = "palmerpenguins")
```

### Write a short desciption of the "penguins" dataset

* The dataset "penguins" have 344 samples. There are 8 variables in total: species, the island the each penguin lives on, the bill length, the bill depth, the flipper length, body mass, sex, and year (of their birth, I suppose). There are some missing values in each variable.

* The size of the dataset: there are 344 rows and 8 columns in this dataset.(Please refer to the R codes below.)

```{r}
nrow(penguins)
ncol(penguins)
```
* The mean flipper length is 200.9152 mm. (Please refer to the R codes below.)

```{r}
mean(penguins$flipper_length_mm, na.rm = TRUE)
```
### Make a scatterplot and export my first scatterplot to my project directory

```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color(species))) + geom_point()
ggsave("scatter_plot_hw1_jn2855.pdf", height = 4, width = 6)
```

## Problem 2

### Create a dataframe 

```{r}
hw1_df = tibble(
  norm_hw1 = rnorm(10),
  norm_hw1_pos = norm_hw1 > 0,
  vec_char_hw1 = c("When", "practicing", "coding", "it", "does", "take", "a", "lot", "of", "time"),
  vec_fac_hw1 = factor(c("Easy", "Medium", "Advanced", "Advanced", "Medium", "Easy", "Advanced", "Advanced", "Advanced", "Advanced"))
)
```

### Take the mean of each variable in my dataframe

```{r}
mean(pull(hw1_df, norm_hw1))
mean(pull(hw1_df, norm_hw1_pos))
mean(pull(hw1_df, vec_char_hw1))
mean(pull(hw1_df, vec_fac_hw1))
```

When I took the mean of each variable, the numeric and logical variables worked, while the character and factor ones didn't.

### Convert variables from one type to another

```{r, results='hide', warning = FALSE}
as.numeric(hw1_df$norm_hw1_pos)
as.numeric(hw1_df$vec_char_hw1)
as.numeric(hw1_df$vec_fac_hw1)
```

Only the logical variable can be converted to a numeric one. I suppose it's because "TRUE" and "FALSE" in logical variables can be indicated as "1" and "0" respectively, and this is also why I could only take the mean of the numeric and logical variables.
